---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.retina=2,
  fig.path = "README-"
)
```

`htmltidy` — Clean up gnarly HTML/XML

Inspired by [this SO question](http://stackoverflow.com/questions/37061873/identify-a-weblink-in-bold-in-r) and because there's a great deal of cruddy HTML out there that needs fixing to use properly when scraping data.

NOTE: Requires [`libtidy`](http://www.html-tidy.org/) and presently is super-basic (no way to set options and pretty much only does HTML)

`brew install tidy-html5` on OS X to get this to work. You'll have to do a bit more leg-work to get it to work on linux (`apt-get install libtidy-dev` on Ubuntu sticks the library in a `tidy` subdir off `/usr/lib` and I don't have a `configure` script setup yet).

**SEEKING COLLABORATORS**

This works enough for me to use in a pinch. It should be straightforward (but tedious) to:

- enable passing options in a `list`
- bundle `libtidy` _with the package_ and get it to work on Windows, linux & MacOS as the library compiles on all three with the necessary tools.

The following functions are implemented:

- `tidy` : Clean up gnarly HTML/XML

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/htmltidy")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(htmltidy)

# current verison
packageVersion("htmltidy")

cat(tidy("<b><p><a href='http://google.com'>google &gt</a></p></b>"))
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
