---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.retina=2,
  fig.path = "README-"
)
```

`htmltidy` — Clean up gnarly HTML/XML

NOTE: Requires [`libtidy`](http://www.html-tidy.org/) and presently is super-basic (no way to set options and pretty much only does HTML)

The following functions are implemented:

- `tidy` : Clean up gnarly HTML/XML

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/htmltidy")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(htmltidy)

# current verison
packageVersion("htmltidy")

cat(tidy("<b><p><a href='http://google.com'>google &gt</a></p></b>"))
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
