---
output: rmarkdown::github_document
---
[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/htmltidy.svg?branch=master)](https://travis-ci.org/hrbrmstr/htmltidy) [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/htmltidy)](https://cran.r-project.org/package=htmltidy) ![downloads](http://cranlogs.r-pkg.org/badges/grand-total/htmltidy)


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  fig.retina=2,
  fig.path = "README-"
)
```

`htmltidy` — Clean up gnarly HTML/XHTML

Inspired by [this SO question](http://stackoverflow.com/questions/37061873/identify-a-weblink-in-bold-in-r) and because there's a great deal of cruddy HTML out there that needs fixing to use properly when scraping data.

It relies on a locally included version of [`libtidy`](http://www.html-tidy.org/) and works on macOS, Linux & Windows.

The following functions are implemented:

- `tidy_html` : Tidy or "Pretty Print" HTML/XHTML Documents

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/htmltidy")
```

```{r echo=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE}
library(htmltidy)

# current verison
packageVersion("htmltidy")

library(XML)
library(xml2)
library(httr)
library(purrr)
```

This is really "un-tidy" content:

```{r message=FALSE, warning=FALSE}
res <- GET("http://rud.is/test/untidy.html")
cat(content(res, as="text"))
```

Let's see what `tidy_html()` does to it:

```{r message=FALSE, warning=FALSE}
cat(tidy_html(content(res, as="text"), list(TidyDocType="html5", TidyWrapLen=200)))
```

NOTE: you could also just have done:

```{r message=FALSE, warning=FALSE}
cat(tidy_html(url("http://rud.is/test/untidy.html"), 
              list(TidyDocType="html5", TidyWrapLen=200)))
```

You'll see that this differs substantially from the mangling `libxml2` does (via `read_html()`):

```{r message=FALSE, warning=FALSE}
pg <- read_html("http://rud.is/test/untidy.html")
cat(toString(pg))
```

It can also deal with "raw" and parsed objects:

```{r message=FALSE, warning=FALSE}
tidy_html(content(res, as="raw"))

tidy_html(content(res, as="text", encoding="UTF-8"))

tidy_html(content(res, as="parsed", encoding="UTF-8"))

tidy_html(htmlParse("http://rud.is/test/untidy.html"))
```

### Testing Options

```{r message=FALSE, warning=FALSE}

opts <- list(TidyDocType="html5",
             TidyMakeClean=TRUE,
             TidyHideComments=TRUE,
             TidyIndentContent=FALSE,
             TidyWrapLen=200)

txt <- "<html>
<head>
      <style>
        p { color: red; }
      </style>
    <body>
          <!-- ===== body ====== -->
         <p>Test</p>

    </body>
        <!--Default Zone
        -->
        <!--Default Zone End-->
</html>"

cat(tidy_html(txt, option=opts))

```

But, you're probably better off running it on plain HTML source.

Since it's C/C++-backed, it's pretty fast:

```{r message=FALSE, warning=FALSE}
book <- readLines("http://singlepageappbook.com/single-page.html")
sum(map_int(book, nchar))
system.time(tidy_book <- tidy_html(book))
```

(It's usually between 20 & 25 milliseconds to process those 202 kilobytes of HTML.) Not too shabby.

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
